---
title: 'Week 9 Coding Part 1: Multiple Linear regression continued'
author: "Elmera Azadpour"
date: "11/30/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(GGally)
library(stargazer)
```

## Data visualization using 'GGally' function to explore relationships and correllation values
```{r, message=FALSE, warning=FALSE}
penguins %>% 
  ggpairs()
```

## Let's parse this into chunks that are a bit more digestable 
```{r, message=FALSE, warning=FALSE}
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color = species))
# looks like within groups, between quantitve vairables, linear relationship seems to make sense
# doesn't look like lots of variables are highly correlated, except for maybe flipper length and body mass -- where the overall correlation is 0.871 and highest is Gentoo with 0.7. 
# not super high correlations to cause concerns about colinearity 
```

## Build a few different models: penguin mass as dependent variable
```{r}
# 1) predictor vairbles: flipper length and species
lm1 <- lm(body_mass_g ~ flipper_length_mm + species, data = penguins)
lm1

# 2) flipper length, species and sex
lm2 <- lm(body_mass_g ~ flipper_length_mm + species + sex, data = penguins)
lm2

# 3) flipper length, species, sex and bill length
lm3 <- lm(body_mass_g ~ flipper_length_mm + species + sex + bill_length_mm, data = penguins)
lm3

# 4) flipper length, species, sex, bill length and island
lm4 <- lm(body_mass_g ~ flipper_length_mm + species + sex + bill_length_mm + island, data = penguins)
lm4
```

## Looking at model AIC scoring, lower AIC = better the balance/model
```{r}
AIC(lm1)
AIC(lm2)
AIC(lm3) # AIC, based on these 4 models, is lowest = best balance of model fit and model complexity
AIC(lm4) # adding this was not worth the increased complexity
```

## Use 'stargazer' package for a table with multiple model outputs 
```{r, results = 'asis'}
stargazer(lm1, lm3, lm4, type = "html")
```

## Omitted variable bias
```{r}
ggplot(penguins, aes(x= flipper_length_mm, 
                     y= bill_depth_mm)) +
  geom_point() +
  geom_smooth(method = "lm")
```

## Let's incldue species this time though
```{r}
ggplot(penguins, aes(x= flipper_length_mm, 
                     y= bill_depth_mm,
                     group = species)) +
  geom_point(aes(color = species)) +
  geom_smooth(method = "lm")
```
## END OF PART 1 - EA 
